### 2020-05-07 figure2.tex
Make talk pictures downstream of figure2
done

% Created by tikzDevice version 0.12.3 on 2020-05-04 03:09:56
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76, 86.93) --
	(570.16, 86.93);

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76,143.33) --
	(570.16,143.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76,199.73) --
	(570.16,199.73);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (365.46,144.28) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (409.96,144.28) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (454.46,144.28) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.96,144.28) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (543.46,142.60) circle (  5.71);

\path[draw=drawColor,line width= 2.3pt,line join=round] (365.46,144.28) --
	(365.46,144.28);

\path[draw=drawColor,line width= 2.3pt,line join=round] (365.46,144.28) --
	(365.46,144.28);

\path[draw=drawColor,line width= 2.3pt,line join=round] (365.46,144.28) --
	(365.46,144.28);

\path[draw=drawColor,line width= 2.3pt,line join=round] (409.96,185.68) --
	(409.96,185.68);

\path[draw=drawColor,line width= 2.3pt,line join=round] (409.96,185.68) --
	(409.96,116.29);

\path[draw=drawColor,line width= 2.3pt,line join=round] (409.96,116.29) --
	(409.96,116.29);

\path[draw=drawColor,line width= 2.3pt,line join=round] (454.46,192.88) --
	(454.46,192.88);

\path[draw=drawColor,line width= 2.3pt,line join=round] (454.46,192.88) --
	(454.46,106.80);

\path[draw=drawColor,line width= 2.3pt,line join=round] (454.46,106.80) --
	(454.46,106.80);

\path[draw=drawColor,line width= 2.3pt,line join=round] (498.96,209.81) --
	(498.96,209.81);

\path[draw=drawColor,line width= 2.3pt,line join=round] (498.96,209.81) --
	(498.96, 58.12);

\path[draw=drawColor,line width= 2.3pt,line join=round] (498.96, 58.12) --
	(498.96, 58.12);

\path[draw=drawColor,line width= 2.3pt,line join=round] (543.46,253.19) --
	(543.46,253.19);

\path[draw=drawColor,line width= 2.3pt,line join=round] (543.46,253.19) --
	(543.46, 51.75);

\path[draw=drawColor,line width= 2.3pt,line join=round] (543.46, 51.75) --
	(543.46, 51.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56, 82.52) {2.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56,138.92) {3.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56,195.32) {3.4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76, 86.93) --
	(338.76, 86.93);

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76,143.33) --
	(338.76,143.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76,199.73) --
	(338.76,199.73);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-05-07 17:13:04
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76, 44.63) --
	(570.16, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76, 85.31) --
	(570.16, 85.31);

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76,125.98) --
	(570.16,125.98);

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76,166.65) --
	(570.16,166.65);

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76,207.32) --
	(570.16,207.32);

\path[draw=drawColor,line width= 0.8pt,line join=round] (338.76,247.99) --
	(570.16,247.99);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (365.46,126.52) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (409.96,126.52) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (454.46,126.52) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.96,126.52) circle (  5.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (543.46,125.55) circle (  5.71);

\path[draw=drawColor,line width= 2.3pt,line join=round] (365.46,126.52) --
	(365.46,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] (365.46,126.52) --
	(365.46,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] (365.46,126.52) --
	(365.46,126.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] (409.96,150.41) --
	(409.96,150.41);

\path[draw=drawColor,line width= 2.3pt,line join=round] (409.96,150.41) --
	(409.96,110.38);

\path[draw=drawColor,line width= 2.3pt,line join=round] (409.96,110.38) --
	(409.96,110.38);

\path[draw=drawColor,line width= 2.3pt,line join=round] (454.46,154.56) --
	(454.46,154.56);

\path[draw=drawColor,line width= 2.3pt,line join=round] (454.46,154.56) --
	(454.46,104.90);

\path[draw=drawColor,line width= 2.3pt,line join=round] (454.46,104.90) --
	(454.46,104.90);

\path[draw=drawColor,line width= 2.3pt,line join=round] (498.96,164.33) --
	(498.96,164.33);

\path[draw=drawColor,line width= 2.3pt,line join=round] (498.96,164.33) --
	(498.96, 76.82);

\path[draw=drawColor,line width= 2.3pt,line join=round] (498.96, 76.82) --
	(498.96, 76.82);

\path[draw=drawColor,line width= 2.3pt,line join=round] (543.46,189.36) --
	(543.46,189.36);

\path[draw=drawColor,line width= 2.3pt,line join=round] (543.46,189.36) --
	(543.46, 73.14);

\path[draw=drawColor,line width= 2.3pt,line join=round] (543.46, 73.14) --
	(543.46, 73.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56, 40.23) {2.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56, 80.90) {2.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56,121.57) {3.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56,162.24) {3.5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56,202.91) {4.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.28] at (331.56,243.58) {4.5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76, 44.63) --
	(338.76, 44.63);

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76, 85.31) --
	(338.76, 85.31);

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76,125.98) --
	(338.76,125.98);

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76,166.65) --
	(338.76,166.65);

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76,207.32) --
	(338.76,207.32);

\path[draw=drawColor,line width= 0.8pt,line join=round] (334.76,247.99) --
	(338.76,247.99);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,289.08);
\definecolor{drawColor}{RGB}{0,0,0}
